### 2025-07-22 paper/sections/other/main_results.qmd
finished table and rerendered preprint

using CTExperiments
using CTExperiments.CairoMakie
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.StatsBase
using Random
using Serialization

@@

df = final_params(res_dir)
float_cols = ["decision_threshold", "lambda_energy_reg"]
get_table_inputs(df, nothing; backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; table_type=:tabular, formatters=PrettyTables.ft_round(2, findall([x in float_cols for x in names(df)])))
```

@@

```{julia}
plt = CTExperiments.plot_performance(res_dir, eps=range(0.0, 0.1, length=10) |> collect, adversarial=true, byvars=["objective", "eps"], drop_synthetic=false)
plt_out = draw(plt, figure=(size=(1000, 150),), axis=(yticks=[0.0,0.5,1.0], limits=(nothing, (0,1)), xticklabelsvisible=false, xticksvisible=false))
save("paper/figures/acc.png", plt_out; px_per_unit=3)
```

@@

```{julia}
lvls = [0.90, 0.95, 0.99]

@@

```{julia}
#| output: asis
#| label: tbl-ci
#| tbl-cap: "Confidence Intervals"

df = Serialization.deserialize("paper/experiments/output/ci.jls")
df = select(df, :variable, :dataset, :full, :vanilla, "99.0%")
df = transform(df, "99.0%" => AsTable) |>
    df -> select(df, Not("99.0%"))
rename!(df, :dataset => :data, :x1 => :LB, :x2 => :UB)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...]
)

@@

>>>>

using CTExperiments
using CTExperiments.CairoMakie
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.PrettyTables
using CTExperiments.StatsBase
using Random
using Serialization

@@

df = final_params(res_dir)
float_cols = ["decision_threshold", "lambda_energy_reg"]
get_table_inputs(df, nothing; backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false, table_type=:tabular, formatters=PrettyTables.ft_round(2, findall([x in float_cols for x in names(df)])))
```

@@

plt = CTExperiments.plot_performance(res_dir, eps=range(0.0, 0.1, length=10) |> collect, adversarial=true, byvars=["objective", "eps"], drop_synthetic=false)
plt_out = draw(plt, figure=(size=(1000, 150),), axis=(yticks=[0.0,0.5,1.0], limits=(nothing, (0,1)), xticklabelsvisible=false, xticksvisible=false))
save("paper/figures/acc.png", plt_out; px_per_unit=3)
```

@@

lvls = [0.90, 0.95, 0.99]

@@

::: {#tbl-ci}

df = Serialization.deserialize("paper/experiments/output/ci.jls")
df = select(df, :variable, :measure, :dataset, :full, :vanilla, "99.0%")
df.variable = (x -> LatexCell(replace(x.data, " \$(-%)\$" => ""))).(df.variable)
sort!(df, [:measure, :dataset])
df = select(df, Not(:measure))
df = transform(df, "99.0%" => AsTable) |>
    df -> select(df, Not("99.0%"))
rename!(df, :dataset => :data, :x1 => :LB, :x2 => :UB, :full => :CT, :vanilla => :BL)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
    sort_by_data = false,
    hlines = :none,
)

@@

Mean outcomes for **CT** and **BL** along with bootstrapped confidence intervals (99%) for difference in mean outcomes grouped by dataset and evaluation metric. Column **LB** and **UB** show the lower and upper bound of the intervals, respectively, and computed using the percentile method. The underlying counterfactual evaluations are the same as the ones used to produce @tbl-main.
